---
title: "Linting Gong_hw7"
author: "Linting Gong"
date: "2016/11/3"
output: html_document
---

##Comments: It is always good to include one test case to show how your code works. After the study of your code, there is one function "plot_density_count" is not included, have you include the corresponding package? If yes, you need study the functiona and the structure of your function.

```{r setup, include=FALSE}
```{r }
library(ggplot2)
library(grid)

explore <- function(data, plotswitch = "off", threshold = 0, vector = NULL) {
  #Function explore is a main function given all subfunctions result
  #we need to run subfunctions first before run this main function
  
  #inpurt:(four Parameters)
  #data: a dataframe
  #plotswitch: a plot switch that can accept three values 
  #threshold: A threshold cut of value between 0 and 1 for correlations
  #vector: bin numbers of histograms. (use the default bin size if vector is not provided)
  
  #Output&Returns:
  
  Freq_table <- freq_table (data) #frequency table
  
  Summary_num <- summary_num (data) #statistics table
  
  R_squared <- r_squared (data) #r-sqaured values
  
  Pearson_coe <- pearson_coe (data, threshold) #pearson correlation coefficient
  
  plot_density_count(data,plotswitch,vector) #plot density and count histograms
  
  plot_gray (data, plotswitch) #plot gray bar
  
  new_result=list(Freq_table, Summary_num, R_squared, Pearson_coe) #new list try to combine all data result 
  
  return (new_result)
  
}




#1
freq_table <- function(data){
# funcion: freqTable 
# This fucntion takes in a dataframe and returns a frequency table
# for every categorical and logical variable.
# Input: dataframe, the data that we are using
# Output: a frequency table.
  data_cat <- c(data[sapply(data,is.factor)],data[sapply(data,is.logical)])
    #select categorical and logical variable
  return (sapply(data_cat,table)) #return a table
}

##2
#a)
summary_num <- function(data){
# function: sumTable
# This fucntion takes in a dataframe and returns a summary statistics table for each numerical variable.
# Input: dataframe, the data that we are using
# Output: a summary statistics table for each numeric variable in the dataframe.
  data_num=data[sapply(data,is.numeric)] #select which column is numeric 
  return (summary(data_num)) #return summary statistics
}

#b).
# function: rSqaure
# This fucntion fits a model on two variables in a dataframe and returns the r square value.
# Input: a data frame that contains each pair of column names in
#the first column (name the column "Variable Pairs") and 
#the associated r-square value in the second column (name the
#column "R-Square").
# Input:  dataframe, the data that we are using
# Output:a new dataframe that contains each pair of column names and corresponding r-square value

r_squared <- function(data) {
  data_num <- data[sapply(data, is.numeric)] # Select the numeric data
  colname <- colnames(data_num) # extract column names
  pairwise_rsquared <- c()  # create a null vector to store the R squares later
  pairwise_names <- c() # # create a null vector to store the names later
  for (i in 1:(length(colname)-1)) {
    for (j in (i+1):length(colname)) { #two column names
      num_rsqaured <- summary(lm(data_num[,i]~data_num[,j]))$r.squared
        # get r-squared data using linear model r.squared
      pairwise_names <- c(pairwise_names, paste(colname[i], colname[j], sep="-"))
        # add pairnames to pairwise_names
      pairwise_rsquared <- c(pairwise_rsquared, num_rsqaured)
        # add r-squared data to pairwise_r_squared
    }
  }
  data_rsquared <- data.frame(pairwise_names, pairwise_rsquared)
  colnames(data_rsquared) <- c("Variable Pairs", "R-squared")
  return (data_rsquared) # return the newly generated data as a data.frame
}  

#c).
# function: pearCoefs
# This fucntion takes in a dataframe, a threshold and returns a data frame
# that contains each pair of column names in the first column (the column name is "Variable Pairs") and correlation coefficient (Pearson) for all coefficientsnwhose absolute value is greater than the correlation threshold in the second column
# Input: dataframe, the data that we are using
# threshold, a number which is the threshold
# Output: a data frame as described above
pearson_coe <- function(data, threshold = 0) {
  data_num <- data[sapply(data, is.numeric)] # select numeric data
  comb_names <- combn(colnames(data_num), 2) # combinations of all names
  pairwise_names <- paste(comb_names[1,], comb_names[2, ], sep = "-") 
    # add "-" in names e.g. x-y
  temp <- cor(data_num, method = "pearson")
    # derive pearson correlation coefficient data using cor function
  cor_data <- temp[which(lower.tri(temp))]  
    # use data in lower triangular of matrix to aviod double-use same data
  dfm_new <- data.frame(pairwise_names, cor_data)
    # create a new dataframe data_coe
  dfm_new <- subset(dfm_new, abs(cor_data) > threshold)
    # select absolute value of correlation greater than threshold
  colnames(dfm_new) <- c("Variable Pairs", "Pearson Exceeds Threshold")
  return(dfm_new)
}
```


